Inference for multivariate peaks over threshold models

### 2021-10-30 evaluation.tex
updates

{\em Proof:}
When $\bm{a}$ and $\bm{b}$ are on the same face, then $g$ is the Euclidean distance, which is a 
  negative definite kernel.  When $\bm{a}$ and $\bm{b}$ are on separate
  faces, we have that $g(\bm{a}, \bm{b}) = g(\bm{b}, \bm{a})$ due to the uniqueness of $\bm{c}$ and the symmetry of the Euclidean distance. Additionally, given $n$ and  collection $\alpha_1,\ldots,\alpha_n\in{\mathbb R}$ such that  $\sum_{i = 1}^n\alpha_i = 0$, then
  \begin{equation*}
    \begin{aligned}
      \sum_{i = 1}^n\sum_{j = 1}^n \alpha_i\alpha_j g(\bm{x}_1,\bm{x}_2) &= \sum_{i = 1}^n\sum_{j = 1}^n \alpha_i\alpha_j \bigg[\pnorm{\bm{c} - \bm{x}_1}{2} + \pnorm{\bm{x}_2 - \bm{c}}{2}\bigg]\\
      &= \sum_{i = 1}^n\sum_{j = 1}^n \alpha_i\alpha_j\pnorm{\bm{c} - \bm{x}_1}{2} + \sum_{i = 1}^n\sum_{j = 1}^n \alpha_i\alpha_j\pnorm{\bm{x}_2 - \bm{c}}{2} \leq0,
    \end{aligned}
  \end{equation*}
  as the Euclidean norm is a negative definite kernel.$\hfill\Box$
Evaluating $g$ as defined in Proposition \ref{prop:g} requires the solution of a $d-2$-dimensional 
  optimization problem in order to obtain $\bm{c}$.  However, a computationally easier \makenote{rewrite sentence} method exists.
\begin{prop}
    Let $\bm{a} \in {\mathbb C}_{\ell}^{d-1}$, and $\bm{b} \in {\mathbb C}_{\jmath}^{d-1}$.  The 
  rotation $P_{\jmath\ell}(\cdot)$ required to move the $\jmath$th face along the $\ell$th axis 
  produces the vector $\bm{b}^\prime$, where
  \begin{equation}
    \label{eqn:rotation}
    P_{\jmath\ell}(\bm{b}) = \bm{b}^{\prime}_i = 
    \begin{cases}
        b_{i} &\text{for }i\neq \jmath,\ell\\
        1 &\text{for }i = \ell\\
        2 - b_{\ell} &\text{for }i = \jmath
    \end{cases}.
  \end{equation}
  Then $g(\bm{a},\bm{b}) = \pnorm{\bm{a} - \bm{b}^{\prime}}{2}$.
\end{prop}
{\em Proof:}
Note that for 
  $\bm{c} \in {\mathbb C}_{\jmath\ell}^{d-2} = {\mathbb C}_{\jmath}^{d-1}\cap{\mathbb C}_{\ell}^{d-1}$,
  $P_{\jmath\ell}(\bm{c}) = \bm{c}$.  Then
  \begin{equation*}
     \pnorm{\bm{b} - \bm{c}}{2} = \pnorm{P_{\jmath\ell}(\bm{b} - \bm{c})}{2} = \pnorm{\bm{b}^{\prime} - \bm{c}}{2},
  \end{equation*}
  as rotations preserve Euclidean norms.  Then,
  \begin{equation*}
    \begin{aligned}
    g(\bm{a}, \bm{b}) &= \pnorm{\bm{a} - \bm{c}}{2} + \pnorm{\bm{b} - \bm{c}}{2}\\
    &= \pnorm{\bm{a} - \bm{c}}{2} + \pnorm{\bm{b}^{\prime} - \bm{c}}{2} = \pnorm{\bm{a} - \bm{b}^{\prime}}{2}
    \end{aligned}
  \end{equation*}
  when $\bm{c} \in \overrightarrow{\bm{a}\bm{b}^{\prime}}$, as the lower bound of the triangle inequality.  We have already declared $\bm{c}\in{\mathbb C}_{\jmath\ell}^{d-2}$, so it must reside at $\overrightarrow{\bm{a}\bm{b}^{\prime}}\cap{\mathbb C}_{\jmath\ell}^{d-2}$.  Because the straight line between $\bm{a}$ and $\bm{b}^{\prime}$ passes through this point without further analysis, the optimization of $\bm{c}$ is accomplished \emph{en passant}.$\hfill\Box$

>>>>

{\em Proof:}
When $\bm{a}$ and $\bm{b}$ are on the same face, then $g$ is the Euclidean distance, which is a 
  negative definite kernel.  When $\bm{a}$ and $\bm{b}$ are on separate
  faces, we have that $g(\bm{a}, \bm{b}) = g(\bm{b}, \bm{a})$ due to the uniqueness of $\bm{c}$ and the symmetry of the Euclidean distance. Additionally, given $n$ and  collection $\alpha_1,\ldots,\alpha_n\in{\mathbb R}$ such that  $\sum_{i = 1}^n\alpha_i = 0$, then
  \begin{equation*}
    \begin{aligned}
      \sum_{i = 1}^n\sum_{j = 1}^n \alpha_i\alpha_j g(\bm{x}_1,\bm{x}_2) &= \sum_{i = 1}^n\sum_{j = 1}^n \alpha_i\alpha_j \bigg[\pnorm{\bm{c} - \bm{x}_1}{2} + \pnorm{\bm{x}_2 - \bm{c}}{2}\bigg]\\
      &= \sum_{i = 1}^n\sum_{j = 1}^n \alpha_i\alpha_j\pnorm{\bm{c} - \bm{x}_1}{2} + \sum_{i = 1}^n\sum_{j = 1}^n \alpha_i\alpha_j\pnorm{\bm{x}_2 - \bm{c}}{2} \leq0,
    \end{aligned}
  \end{equation*}
  as the Euclidean norm is a negative definite kernel.$\hfill\Box$

Evaluating $g$ as defined in Proposition \ref{prop:g} requires the solution of a $d-2$-dimensional 
  optimization problem in order to obtain $\bm{c}$.  However, a computationally easier \makenote{rewrite sentence} method exists.
\begin{prop}
    Let $\bm{a} \in {\mathbb C}_{\ell}^{d-1}$, and $\bm{b} \in {\mathbb C}_{\jmath}^{d-1}$.  The 
  rotation $P_{\jmath\ell}(\cdot)$ required to move the $\jmath$th face along the $\ell$th axis 
  produces the vector $\bm{b}^\prime$, where
  \begin{equation}
    \label{eqn:rotation}
    P_{\jmath\ell}(\bm{b}) = \bm{b}^{\prime}_i = 
    \begin{cases}
        b_{i} &\text{for }i\neq \jmath,\ell\\
        1 &\text{for }i = \ell\\
        2 - b_{\ell} &\text{for }i = \jmath
    \end{cases}.
  \end{equation}
  Then $g(\bm{a},\bm{b}) = \pnorm{\bm{a} - \bm{b}^{\prime}}{2}$.
\end{prop}
{\em Proof:}
Note that for 
  $\bm{c} \in {\mathbb C}_{\jmath\ell}^{d-2} = {\mathbb C}_{\jmath}^{d-1}\cap{\mathbb C}_{\ell}^{d-1}$,
  $P_{\jmath\ell}(\bm{c}) = \bm{c}$.  Then
  \begin{equation*}
     \pnorm{\bm{b} - \bm{c}}{2} = \pnorm{P_{\jmath\ell}(\bm{b} - \bm{c})}{2} = \pnorm{\bm{b}^{\prime} - \bm{c}}{2},
  \end{equation*}
  as rotations preserve Euclidean norms.  Then,
  \begin{equation*}
    \begin{aligned}
    g(\bm{a}, \bm{b}) &= \pnorm{\bm{a} - \bm{c}}{2} + \pnorm{\bm{b} - \bm{c}}{2}\\
    &= \pnorm{\bm{a} - \bm{c}}{2} + \pnorm{\bm{b}^{\prime} - \bm{c}}{2} = \pnorm{\bm{a} - \bm{b}^{\prime}}{2}
    \end{aligned}
  \end{equation*}
  when $\bm{c} \in \overrightarrow{\bm{a}\bm{b}^{\prime}}$, as the lower bound of the triangle inequality.  We have already declared $\bm{c}\in{\mathbb C}_{\jmath\ell}^{d-2}$, so it must reside at $\overrightarrow{\bm{a}\bm{b}^{\prime}}\cap{\mathbb C}_{\jmath\ell}^{d-2}$.  Because the straight line between $\bm{a}$ and $\bm{b}^{\prime}$ passes through this point without further analysis, the optimization of $\bm{c}$ is accomplished \emph{en~passant}.$\hfill\Box$

Interpretation of the energy score as we have formulated it here is the same as that of posterior predictive loss: smaller is better.
